Remark on the hypothetical judgment

### 2018-01-04 paper.tex
...

\documentclass[11pt]{amsart}
\usepackage{setspace,url,hyperref}
\usepackage{amssymb,stmaryrd}
\usepackage{proof}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
%\newtheorem{note}[thm]{Note}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\numberwithin{equation}{section}

\def\InputModeColorName{MidnightBlue}
\def\OutputModeColorName{Maroon}
\newcommand\InputMode[1]{{\color{\InputModeColorName}{#1}}}
\newcommand\OutputMode[1]{{\color{\OutputModeColorName}{#1}}}

@@

\author{Jonathan Sterling}
\address{}

\onehalfspacing

@@

What is the proper explanation of intuitionistic hypothetical judgment, and
thence propositional implication? The answer to this question is not clearly
determinate from the writings of Brouwer, Heyting and Kolmogorov, since in
their lifetimes they propounded multiple (sometimes conflicting) explanations
of the hypothetical judgment. To my mind, the determination of an acceptable
explanation must take into account its adequacy for the expression of the bar
theorem and, more generally, the development of an open-ended framework for
transcendental arguments in mathematics.

@@

The judgments and demonstrations are the activity of the subject in performing
and experiencing mathematics. On the other hand, the theory of sets that we have
defined is, to my mind, the correct level at which to \emph{do} mathematics,
where objects are concrete and have an extensional identity. By guaranteeing
pervasive functionality, we have embedded in the rich world of intuitionistic
mathematics a haven invulnerable to the paradoxes that arise from failures of
extensionality, such as Diaconescu's theorem \cite{martin-lof:2009, sterling:diaconescu}.

>>>>

\documentclass[11pt]{article}
\usepackage[tt=false]{libertine}
\usepackage{url,hyperref}
\usepackage{amsmath,amsthm,amssymb,stmaryrd}
\usepackage{proof}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{sectsty}
\allsectionsfont{\sffamily}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
%\newtheorem{note}[thm]{Note}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}

\newcommand\InputMode[1]{#1}
\newcommand\OutputMode[1]{#1}

@@

\author{Jonathan Sterling}
\date{Fall 2015}

@@

  What is the proper explanation of intuitionistic hypothetical judgment, and
  thence propositional implication? The answer to this question is not clearly
  determinate from the writings of Brouwer, Heyting and Kolmogorov, since in
  their lifetimes they proposed multiple (sometimes conflicting) explanations
  of the hypothetical judgment. The determination of an acceptable explanation
  must take into account its adequacy for the expression of the bar theorem
  and, more generally, the development of an open-ended framework for
  transcendental arguments in mathematics.

@@

The judgments and demonstrations are the activity of the subject in performing
and experiencing mathematics. On the other hand, the theory of sets that we have
defined is the correct level at which to \emph{do} mathematics,
where objects are concrete and have an extensional identity. By guaranteeing
pervasive functionality, we have embedded in the rich world of intuitionistic
mathematics a haven invulnerable to the paradoxes that arise from failures of
extensionality, such as Diaconescu's theorem \cite{martin-lof:2009, sterling:diaconescu}.
